---
title: "Identificacion DMR Genero"
author: "Ana Diez Borge"
date: "7 de diciembre de 2020"
output: html_document
---

```{r Cargamos datos de metilación}
Data_dir <- "~/Master UOC - Bioinfo y bioestadistica/TFM/Rstudio"
Results_dir <- "~/Master UOC - Bioinfo y bioestadistica/TFM/Rstudio/Results"
setwd(Data_dir)
coad_data = readRDS(file = "coad_data.RDS")
lihc_data = readRDS(file = "lihc_data.RDS")
paad_data = readRDS(file = "paad_data.RDS")
luad_data = readRDS(file = "luad_data.RDS")
```

```{r Matriz modelo y contraste PAAD}
#BiocManager::install("DMRcate")
library(DMRcate)
type_paad <- factor(paad_data$gender)
design_paad <- model.matrix(~type_paad)
myannotation_paad <- cpg.annotate("array", assay(paad_data), arraytype = "450K",
analysis.type="differential", design=design_paad, coef=2)
```
Your contrast returned 19 individually significant probes; a small but real effect. Consider manually setting the value of pcutoff to return more DMRs, but be warned that doing this increases the risk of Type I errors.

```{r Matriz modelo y contraste LIHC}
library(DMRcate)
type_lihc <- factor(lihc_data$gender)
design_lihc <- model.matrix(~type_lihc)
myannotation_lihc <- cpg.annotate("array", assay(lihc_data), arraytype = "450K",
analysis.type="differential", design=design_lihc, coef=2)
```
Your contrast returned 337 individually significant probes. We recommend the default setting of pcutoff in dmrcate().

```{r Matriz modelo y contraste COAD}
library(DMRcate)
type_coad <- factor(coad_data$gender)
design_coad <- model.matrix(~type_coad)
myannotation_coad <- cpg.annotate("array", assay(coad_data), arraytype = "450K",
analysis.type="differential", design=design_coad, coef=2)
```
Your contrast returned 108 individually significant probes. We recommend the default setting of pcutoff in dmrcate().

```{r Matriz modelo y contraste LUAD}
library(DMRcate)
type_luad <- factor(luad_data$gender)
design_luad <- model.matrix(~type_luad)
myannotation_luad <- cpg.annotate("array", assay(luad_data), arraytype = "450K",
analysis.type="differential", design=design_luad, coef=2)
```
Your contrast returned 62 individually significant probes; a small but real effect. Consider manually setting the value of pcutoff to return more DMRs, but be warned that doing this increases the risk of Type I errors.

```{r}
dmrcoutput_paad <- dmrcate(myannotation_paad, lambda=1000, C=2)
dmrcoutput_paad
dmrcoutput_lihc <- dmrcate(myannotation_lihc, lambda=1000, C=2)
dmrcoutput_coad <- dmrcate(myannotation_coad, lambda=1000, C=2)
dmrcoutput_luad <- dmrcate(myannotation_luad, lambda=1000, C=2)
```
GRanges object with 3 ranges and 8 metadata columns:
      seqnames              ranges strand |   no.cpgs min_smoothed_fdr
         <Rle>           <IRanges>  <Rle> | <integer>        <numeric>
  [1]    chr13 114239234-114239697      * |         2      3.15921e-35
  [2]     chr2 208576002-208577105      * |        10      1.23196e-68
  [3]    chr10       530836-531465      * |         6      1.93788e-21
        Stouffer       HMFDR      Fisher   maxdiff   meandiff
       <numeric>   <numeric>   <numeric> <numeric>  <numeric>
  [1] 0.00353578 2.19064e-04 0.000543597 -0.148521 -0.0866364
  [2] 1.00000000 1.83045e-06 0.054828307 -0.159696 -0.0145032
  [3] 1.00000000 9.79207e-01 0.999999996  0.199757  0.1514052
                               overlapping.genes
                                     <character>
  [1]                             SNORD36, TFDP1
  [2] CCNYL1, SCARNA6, SNORD39, SNORA75, SNORA48
  [3]                                      DIP2C
  -------
  seqinfo: 3 sequences from an unspecified genome; no seqlengths

```{r}
results.ranges_paad <- extractRanges(dmrcoutput_paad, genome = "hg19")
results.ranges_lihc <- extractRanges(dmrcoutput_lihc, genome = "hg19")
results.ranges_coad <- extractRanges(dmrcoutput_coad, genome = "hg19")
results.ranges_luad <- extractRanges(dmrcoutput_luad, genome = "hg19")
```

```{r DMR plot PAAD}
library(DMRcate)
groups <- c(female="magenta", male="forestgreen")
cols_paad <- groups[as.character(type_paad)]
DMR.plot(ranges=results.ranges_paad, dmr=1, CpGs=assay(paad_data), what="Beta",
arraytype = "450K", phen.col=cols_paad, genome="hg19")
```
Error in simpleLoess(y, x, w, span, degree = degree, parametric = FALSE, : NA/NaN/Inf in foreign function call (arg 1)

```{r DMR plot lihc}
groups_lihc <- c(male="magenta", female="forestgreen")
cols_lihc <- groups[as.character(type_lihc)]
cols_lihc
DMR.plot(ranges=results.ranges_lihc, dmr=1, CpGs=assay(lihc_data), what="Beta",
arraytype = "450K", phen.col=cols_lihc, genome="hg19")
```
Error in .local(GdObject, ...) : Too many stacks to draw. Either increase the device size or limit the drawing to a smaller region.

```{r DMR plot coad}
groups_coad <- c(male="magenta", female="forestgreen")
cols_coad <- groups[as.character(type_coad)]
cols_coad
DMR.plot(ranges=results.ranges_coad, dmr=1, CpGs=assay(coad_data), what="Beta",
arraytype = "450K", phen.col=cols_coad, genome="hg19")
```
Error in h(simpleError(msg, call)) : error in evaluating the argument 'y' in selecting a method for function 'setdiff': error in evaluating the argument 'x' in selecting a method for function 'resize': [[ subscript must be >= 1

```{r DMR plot luad}
groups_luad <- c(male="magenta", female="forestgreen")
cols_luad <- groups[as.character(type_luad)]
cols_luad
DMR.plot(ranges=results.ranges_luad, dmr=1, CpGs=assay(luad_data), what="Beta",
arraytype = "450K", phen.col=cols_luad, genome="hg19")
```
Error in simpleLoess(y, x, w, span, degree = degree, parametric = FALSE, : span is too small

